---
title: "MH_Summary_HW"
author: "Marilyn Harbert"
date: "`r Sys.Date()`"
output: html_document
---

##Project Summary##

Queer people experience domestic violence differently and thus require different information about domestic violence than straight people. In addition, domestic violence is often framed as a heterosexual women's issue, leaving queer people out of information provided about domestic violence. 

My data for this project is articles discussing domestic violence from the Chicago based LGBTQ+ newspaper "The Windy City".

For this project I will conduct topic modeling on phrases related to domestic violence to understand narratives and topics associated with domestic violence in past public information available to LGBT people. I will compute basic statistics on the articles, and look at the most common bigrams for articles discussing queer domestic violence. I will also conduct sentiment analysis, and (unless I am very surprised by the results) write a specific queer critique of sentiment analysis. 

#Codebook# 

I am thinking about how to analyze the topic modeling and bigram generation for this project, and I think I have an initial list of codes I might use to categorize the terms I see in order to make sense of the data. 
- health : terms related to health
- identity : terms related to identity/demographics
- violence : terms that reference violence or abuse directly
- community : terms related to community or non-profit groups
- advocacy : terms related to stopping domestic violence
- location : terms that refer to locations

#Data#

Initial data downloaded in .txt format from Proquest, only top 100 results downloaded. Search was conducted for "domestic violence" AND "LGBTQ+". The publication list for these results was cross-checked with a list of LGBTQ+ publications from Wikipedia to find the LGBTQ+ publication with the most results for these search terms, which was the Chicago based publication "The Windy City". The sample analyzed below is thus the top 100 results of the search in proquest for "domestic violence" from The Windy City. Additionally, the metadata for the articles was downloaded from proquest at the same time. 

Link to initial data: https://github.com/marilynharbert/CompText_Jour/blob/main/docs/Summary_HW/ProQuestDocuments-2024-11-17.txt

##Code## Loading libraries

```{r}
library(tidyverse)
library(pdftools)
library(quanteda)
library(tidytext)
library(rio)
library(readxl)
```

Extracting data from the .txt file

```{r}
# Set the path to your .txt file
file_path <- "../Summary_HW/windycity_dv_1_100.txt"

# Read the .txt file line by line
text <- readLines(file_path)

# Convert the lines into a dataframe, one line per row
gay_dv_articles <- data.frame(text)
```

Extract metadata from excel file
```{r}
metadata_top100_dv_windy_city <- read_excel("~/Code/CompText_Jour/docs/Summary_HW/windycity_dv_1_100.xls")

# create indices
metadata_top100_dv_windy_city <- metadata_top100_dv_windy_city %>%
  mutate(index = row_number())

```

create linked index

```{r}
# Step 2: Combine lines into one single string
text_combined <- paste(text, collapse = "\n")

text_combined <- sub(".*Table of contents", "Table of contents", text_combined)

# Step 3: Split the text by the "End of Document" phrase
documents <- strsplit(text_combined, "____________________________________________________________")[[1]]

# Step 4: Write each section to a new file
output_dir <- "../Summary_HW/article_data_dv/"
for (i in seq_along(documents)) {
  output_file <- file.path(output_dir, paste0("dv_", i, ".txt"))
  writeLines(documents[[i]], output_file)
}

cat("Files created:", length(documents), "\n")

moley_index <- read_lines("../Summary_HW/article_data_dv/dv_1.txt")
# Extract lines 5 to 215
extracted_lines <- moley_index[5:215]

# Print the extracted lines to the console
cat(extracted_lines, sep = "\n")

extracted_lines <- extracted_lines |> 
  as.data.frame() 

# Step 1: Trim spaces and detect rows with titles
cleaned_data <- extracted_lines |>
  mutate(
    # Trim leading and trailing spaces before detection
    trimmed_line = str_trim(extracted_lines),  

    # Detect titles (start with a number and a period)
    is_title = str_detect(trimmed_line, "^\\d+\\. "),  
  )

metadata_top100_dv_windy_city <- metadata_top100_dv_windy_city %>%
  rename(title = Title)

#new title column with trim numbers from titles

cleaned_data <- cleaned_data %>%
  mutate(title = gsub("^\\d+\\.\\s*", "", trimmed_line)) %>%
  filter(title != "") %>%
  filter(title != " ") %>%
  filter(!is.na(title))

# add indecise
cleaned_data <- cleaned_data %>%
  mutate(index = row_number())

# add dates
aligned_data <- cleaned_data %>%
  left_join(metadata_top100_dv_windy_city, by = "index")

# Step 3: Rename columns for clarity
final_data <- aligned_data |>
  #select columns to keep
  select(-c(extracted_lines, StoreId, companies, copyright, issn, language, 
            languageOfSummary, pages, entryDate, DocumentURL, documentFeatures,
            identifierKeywords, startPage, subjectTerms, subjects, FindACopy,
            Database, title.y)) %>%
  #rename to good names
  rename(date = pubdate,
         abstract = Abstract,
         article_type = ArticleType,
         authors = Authors, 
         document_type = documentType,
         place_ofpublication = placeOfPublication, 
         title = title.x)

write_csv(final_data, "../Summary_HW/dv_index_data.csv")

files <- list.files("../Summary_HW/article_data_dv/", pattern="dv.*.txt") %>% 
  as.data.frame() |> 
  rename(filename = 1) |> 
  #create an index with the file name
  mutate(index = str_extract(filename, "\\d+")) |> 
  mutate(index = as.numeric(index))

final_index <- final_data |> 
  inner_join(files, c("index")) |> 
  mutate(filepath = paste0("../Summary_HW/article_data_dv/", filename))
head(final_index)

create_article_text <- function(row_value) {
  
  #row_value is the single argument that is passed to the function
  # Take each row of the dataframe
  temp <- final_index %>%
    slice(row_value)
  
  # Store the filename for  use in constructing articles dataframe
  temp_filename <- temp$filename
  
  # Create a dataframe by reading in lines of a given textfile
  # Add a filename column 
  articles_df_temp <- read_lines(temp$filepath) %>%
    as_tibble() %>%
    mutate(filename = temp_filename)
  
  # Bind results to master articles_df
  # <<- returns to global environment
  articles_df <<- articles_df %>%
    bind_rows(articles_df_temp)
}

# Create empty tibble to store results
articles_df <- tibble()

# Create an array of numbers to loop through, from 1 to the number of rows in our index dataframe 
row_values <- 1:nrow(final_index)

lapply(row_values, create_article_text)

articles_df <- articles_df %>%
  select(filename, sentence=value) %>%
  inner_join(final_index)

articles_df <- articles_df %>%
  slice(-c(2:252)) |> 
  #gets rid of blank rows
    filter(trimws(sentence) != "") 

write.csv(articles_df, "../Summary_HW/dvlinkedindex.csv")
```

get rid of the junk

```{r}
#clean up text column
clean_df <- articles_df %>%
  mutate(text = str_squish(sentence)) %>% #gets rid of leading and trailing spaces + double spaces
  mutate(text = tolower(text)) %>%
  mutate(text = str_replace(text, "startofarticle", "")) %>%
  mutate(text = str_replace(text, "____________________________________________________________", "")) %>%
  mutate(text = gsub("issn:\\s+\\S+", "", text)) %>%
  mutate(text = gsub("http[^ ]*", "http", text)) %>%
  mutate(text = str_replace_all(text, c(
    "copyright" = "",
    "database: proquest central" = "",
    "language of publication: english" = "",
    "document url:\\s+\\S+" = "",
    "proquest document id:\\s+\\S+" = "",
    "publication subject:\\s+\\S+" = "",
    "publication date:\\s+\\S+" = "",
    "publication-type:\\s+\\S+" = "",
    "pages:\\s+\\S+" = "",
    "publication info" = "",
    "last updated:\\s+\\S+" = "",
    "interest periodicals--united states" = "",
    "all rights resesrved" = "",
    "load-date" = "",
    "all rights reserved" = "", 
    "new york times" = "",
    "language: english" = "",
    "author:\\s+\\S+" = "",
    "abstract:\\s+\\S+" = "",
    "links:\\s+\\S+" = "",
    "publication title:\\s+\\S+" = "",
    "volume:\\s+\\S+" = "",
    "issue:\\s+\\S+" = "",
    "publication year:\\s+\\S+" = "",
    "publisher: windy city media group" = "",
    "place of publication: chicago, ill." = "",
    "country of publication: united states, chicago, ill." = "",
    "document type:\\s+\\S+" = "",
    "database: genderwatch" = "",
    "identifier / keyword: y; genderwatch" = "",
    "source type: newspaper" = "",
    "windy city times" = "",
    "umcp.primo.exlibrisgroup.com\\s+\\S+" = "",
    "usmai-umcp.primo.exlibrisgroup.com" = "",
    "id	doi" = "",
    "Links: https://usmai-umcp.primo.exlibrisgroup.com/" = "",
    "windy city media group" = "",
    "city times; chicago, ill." = "",
    "http" = "",
    "document feature" = "",
    "feature photographs" = ""
  ))) 

```

Tokenize the data

```{r}
#Tokenize the data
bitoken_clean_df <- clean_df %>%
  unnest_tokens(bigram, text, token="ngrams", n=2)

bigrams_separated <- bitoken_clean_df %>%
  separate(bigram, c("word1", "word2"), sep = " ")

#remove stop words and 
data(stop_words)
bigrams_separated <- bigrams_separated %>%
  filter(!word1 %in% stop_words$word) %>%
  filter(!word2 %in% stop_words$word) %>%
  filter(word1  != "https") %>%
  filter(word2  != "https") %>%
  filter(!grepl('[0-9]',word1)) %>%
  filter(!grepl('[0-9]',word2)) 
```

Descriptive statistics

```{r}
# number of lines
count_lines <- clean_df %>%
  summarise(count_lines = n())

# number of lines per article
count_lines_index <- clean_df %>%
  group_by(index) %>%
  summarise(count_lines = n())

# number of words per article
count_df <- clean_df %>%
  group_by(index) %>%
  summarise(count_words = str_count(text, '\\S+')) %>%
  summarise(count_lines = sum(count_words))

```

Data Sample

```{r}
head(clean_df, 30)

```

Sample of Data Analysis

Top 20 bigrams

```{r}
bigrams_filtered <- bigrams_separated %>%
  filter(!word1 %in% stop_words$word) %>%
  filter(!word2 %in% stop_words$word)

bigram_ct <- bigrams_filtered %>%
  count(word1, word2, sort = TRUE) %>% 
  filter(!is.na(word1))

top_20_bigrams <- head(bigram_ct, 20)
top_20_bigrams

```

Plot Top 20 Bigrams

```{r}
# bigram needs to be one column
bigram_ct_toplot <- head(bigram_ct,20) %>%
  mutate(bigram = paste0(word1, " ", word2)) %>%
  mutate(n = as.numeric(n))

bi_plot <- ggplot(data=bigram_ct_toplot, aes(fill = n, x = reorder(bigram, n), y = n)) +
  geom_col() +
  scale_y_continuous(breaks = seq(0, 300, by = 25)) +
  labs(y = NULL, 
       x = "Bigram") + 
  coord_flip() +
  ggtitle("Top 20 Bigrams in Articles about Domestic Violence\npublished in The Windy City Times") + 
  theme(legend.position="none") + 
  expand_limits(x = 0, y = 0)

plot(bi_plot)
```

map years
```{r}
year_df <- clean_df %>%
  select(year, index) %>%
  distinct() %>%
  count(year)

year_plot <- ggplot(data=year_df, aes(year, n, fill = n)) +
  geom_col() +
  labs(y = NULL, 
       x = "year") + 
  ggtitle("Articles over time mentioning Domestic Violence\npublished in The Windy City Times") + 
  theme(legend.position="none") 

plot(year_plot)
```
