---
title: "MH_Summary_HW"
author: "Marilyn Harbert"
date: "`r Sys.Date()`"
output: html_document
---

## Project Summary

Queer people experience domestic violence differently and thus require different information about domestic violence than straight people. In addition, domestic violence is often framed as a heterosexual women's issue, leaving queer people out of information provided about domestic violence. 

My data for this project is articles discussing domestic violence from the Chicago based LGBTQ+ newspaper "The Windy City".

For this project I will conduct topic modeling on phrases related to domestic violence to understand narratives and topics associated with domestic violence in past public information available to LGBT people. I will compute basic statistics on the articles, and look at the most common bigrams for articles discussing queer domestic violence. I will also conduct sentiment analysis, and write a specific queer critique of sentiment analysis. 
# Codebook

I am thinking about how to analyze the topic modeling and bigram generation for this project, and I think I have an initial list of codes I might use to categorize the terms I see in order to make sense of the data. 
- health : terms related to health
- identity : terms related to identity/demographics
- violence : terms that reference violence or abuse directly
- community : terms related to community or non-profit groups
- advocacy : terms related to stopping domestic violence
- location : terms that refer to locations

# Data

Initial data downloaded in .txt format from Proquest, only top 100 results downloaded. Search was conducted for "domestic violence" AND "LGBTQ+". The publication list for these results was cross-checked with a list of LGBTQ+ publications from Wikipedia to find the LGBTQ+ publication with the most results for these search terms, which was the Chicago based publication "The Windy City". The sample analyzed below is thus the top 100 results of the search in proquest for "domestic violence" from The Windy City. Additionally, the metadata for the articles was downloaded from proquest at the same time. 

Link to initial data: https://github.com/marilynharbert/CompText_Jour/blob/main/docs/Summary_HW/ProQuestDocuments-2024-11-17.txt

## Code 

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE, results = 'hide')

library(tidyverse)
library(pdftools)
library(quanteda)
library(tidytext)
library(rio)
library(readxl)
library(here)
library(tidytext)
library(tm)
library(topicmodels)
library(reshape2)
library(wordcloud)
library(pals)
library(SnowballC)
library(lda)
library(ldatuning)
library(kableExtra)
library(DT)
library(flextable)
library(remotes)
library(readtext)
library(formattable)
```

### Set options

```{r}
options(stringsAsFactors = F)         # no automatic data transformation
options("scipen" = 100, "digits" = 4) # suppress math annotation
```

### Extracting data from the .txt file

```{r}
# Set the path to your .txt file
file_path <- "../Summary_HW/ProQuestDocuments-2024-11-27 (1).txt"

# Read the .txt file line by line
text <- readLines(file_path)

text <- text[-c(1:4)]

# Convert the lines into a dataframe, one line per row
gay_dv_articles <- data.frame(text)
```

### Extract metadata from excel file

```{r}
metadata <- read_excel("~/Code/CompText_Jour/docs/Summary_HW/ProQuestDocuments-2024-11-27 (1).xls")

# create indices
metadata_dv_windy_city <- metadata %>%
  mutate(index = row_number())
```

### Create linked index

```{r}
# Step 2: Combine lines into one single string
text_combined <- paste(text, collapse = "\n")

# Step 3: Split the text by the "End of Document" phrase
documents <- strsplit(text_combined, "_____________________________________________")[[1]]
### only 213 elements in documents - should be 216 

# Step 4: Write each section to a new file
output_dir <- "../Summary_HW/article_data_dv/"
for (i in seq_along(documents)) {
  output_file <- file.path(output_dir, paste0("dv_", i, ".txt"))
  writeLines(documents[[i]], output_file)
}
### i goes up to 213 

cat("Files created:", length(documents), "\n")

# says it created 213 files

dv_index <- read_lines("../Summary_HW/article_data_dv/dv_1.txt")
# Extract lines 3 to 541
extracted_lines <- dv_index[3:541]

# Print the extracted lines to the console
# cat(extracted_lines, sep = "\n")

extracted_lines <- extracted_lines |> 
  as.data.frame() 

# Step 1: Trim spaces and detect rows with titles
cleaned_data <- extracted_lines |>
  mutate(
    # Trim leading and trailing spaces before detection
    trimmed_line = str_trim(extracted_lines),  

    # Detect titles (start with a number and a period)
    is_title = str_detect(trimmed_line, "^\\d+\\. "),  
  )

metadata_dv_windy_city <- metadata_dv_windy_city %>%
  rename(title = Title)

#new title column with trim numbers from titles

cleaned_data <- cleaned_data %>%
  mutate(title = gsub("^\\d+\\.\\s*", "", trimmed_line)) %>%
  filter(title != "") %>%
  filter(title != " ") %>%
  filter(!is.na(title))

# add indecise
cleaned_data <- cleaned_data %>%
  mutate(index = row_number())

# add dates
aligned_data <- cleaned_data %>%
  left_join(metadata_dv_windy_city, by = "index")

# Step 3: Rename columns for clarity
final_data <- aligned_data |>
  #select columns to keep
  select(-c(extracted_lines, StoreId, companies, copyright, issn, language, 
            languageOfSummary, pages, entryDate, DocumentURL, documentFeatures,
            identifierKeywords, startPage, subjectTerms, subjects, FindACopy,
            Database, title.y)) %>%
  #rename to good names
  rename(date = pubdate,
         abstract = Abstract,
         article_type = ArticleType,
         authors = Authors, 
         document_type = documentType,
         place_ofpublication = placeOfPublication, 
         title = title.x)

write_csv(final_data, "../Summary_HW/dv_index_data.csv")

files <- list.files("../Summary_HW/article_data_dv/", pattern="dv.*.txt") %>% 
  as.data.frame() |> 
  rename(filename = 1) |> 
  #create an index with the file name
  mutate(index = str_extract(filename, "\\d+")) |> 
  mutate(index = as.numeric(index))

final_index <- final_data |> 
  inner_join(files, c("index")) |> 
  mutate(filepath = paste0("../Summary_HW/article_data_dv/", filename))

create_article_text <- function(row_value) {
  #row_value is the single argument that is passed to the function
  # Take each row of the dataframe
  temp <- final_index %>%
    slice(row_value)
  
  # Store the filename for  use in constructing articles dataframe
  temp_filename <- temp$filename
  
  # Create a dataframe by reading in lines of a given textfile
  # Add a filename column 
  articles_df_temp <- read_lines(temp$filepath) %>%
    as_tibble() %>%
    mutate(filename = temp_filename)
  
  # Bind results to master articles_df
  # <<- returns to global environment
  articles_df <<- articles_df %>%
    bind_rows(articles_df_temp)
}

# Create empty tibble to store results
articles_df <- tibble()

# Create an array of numbers to loop through, from 1 to the number of rows in our index dataframe 
row_values <- 1:nrow(final_index)

lapply(row_values, create_article_text)

articles_df <- articles_df %>%
  select(filename, sentence=value) %>%
  inner_join(final_index)

articles_df <- articles_df %>%
  slice(-c(2:533)) |> 
  #gets rid of blank rows
    filter(trimws(sentence) != "") 

write.csv(articles_df, "../Summary_HW/dvlinkedindex.csv")
```

### Cleaning: get rid of the junk! 

```{r}
clean_df <- articles_df %>%
  mutate(text = str_squish(sentence)) %>% #gets rid of leading and trailing spaces + double spaces
  mutate(text = tolower(text)) %>%
  mutate(text = str_replace(text, "startofarticle", "")) %>%
  mutate(text = str_replace_all(text, "__", "")) %>%
  mutate(text = gsub("issn:\\s+\\S+", "", text)) %>%
  mutate(text = gsub("http[^ ]*", "http", text)) %>%
  mutate(text = str_replace_all(text, c(
    "copyright" = "",
    "database: proquest central" = "",
    "language of publication: english" = "",
    "document url:\\s+\\S+" = "",
    "proquest document id:\\s+\\S+" = "",
    "publication subject:\\s+\\S+" = "",
    "publication date:\\s+\\S+" = "",
    "publication-type:\\s+\\S+" = "",
    "pages:\\s+\\S+" = "",
    "publication info" = "",
    "last updated:\\s+\\S+" = "",
    "interest periodicals--united states" = "",
    "all rights resesrved" = "",
    "load-date" = "",
    "all rights reserved" = "", 
    "new york times" = "",
    "language: english" = "",
    "author:\\s+\\S+" = "",
    "abstract:\\s+\\S+" = "",
    "links:\\s+\\S+" = "",
    "publication title:\\s+\\S+" = "",
    "volume:\\s+\\S+" = "",
    "issue:\\s+\\S+" = "",
    "publication year:\\s+\\S+" = "",
    "publisher: windy city media group" = "",
    "place of publication: chicago, ill." = "",
    "country of publication: united states, chicago, ill." = "",
    "document type:\\s+\\S+" = "",
    "database: genderwatch" = "",
    "identifier / keyword: y; genderwatch" = "",
    "source type: newspaper" = "",
    "windy city times" = "",
    "umcp.primo.exlibrisgroup.com\\s+\\S+" = "",
    "usmai-umcp.primo.exlibrisgroup.com" = "",
    "id	doi" = "",
    "Links: https://usmai-umcp.primo.exlibrisgroup.com/" = "",
    "windy city media group" = "",
    "city times; chicago, ill." = "",
    "http" = "",
    "document feature:\\s+\\S+" = "",
    "feature photographs" = "",
    "full text:" = "",
    "city times" = "",
    "subject:\\s+\\S+" = "",
    "company / organization:\\s+\\S+" = "",
    "location:\\s+\\S+" = "",
    "illinois; united states--us; illinois" = "",
    "business indexing term:" = "",
    "ch icago, ill." = "",
    "title" = "", 
    "web site:\\s+\\S+" = ""
  ))) 

# I used Chat GPT to get the regexes in this section 
# Prompts used: 
# # what is the regex for .
# # what is the escape character in regular expressions
# # what R code should I use to remove all strings with "ISSN" and the phrase immediately following that one from a dataset?
# # give me r code to get rid of any characters that come after "http" but before a space in a string
```

### Tokenize the data

```{r}
#Tokenize the data
bitoken_clean_df <- clean_df %>%
  unnest_tokens(bigram, text, token="ngrams", n=2)

bigrams_separated <- bitoken_clean_df %>%
  separate(bigram, c("word1", "word2"), sep = " ")

#remove stop words 
data(stop_words)
bigrams_separated <- bigrams_separated %>%
  filter(!word1 %in% stop_words$word) %>%
  filter(!word2 %in% stop_words$word) %>%
  filter(word1  != "https") %>%
  filter(word2  != "https") %>%
  filter(!grepl('[0-9]',word1)) %>%
  filter(!grepl('[0-9]',word2)) 
```

### Descriptive statistics

```{r}
# number of lines
count_lines <- clean_df %>%
  summarise(count_lines = n())

# number of lines per article
count_lines_index <- clean_df %>%
  group_by(index) %>%
  summarise(count_lines = n())

# number of words per article
count_df <- clean_df %>%
  group_by(index) %>%
  summarise(count_words = str_count(text, '\\S+')) %>%
  summarise(count_lines = sum(count_words))
```

## Top 20 bigrams

```{r}
bigrams_filtered <- bigrams_separated %>%
  filter(!word1 %in% stop_words$word) %>%
  filter(!word2 %in% stop_words$word)

bigram_ct <- bigrams_filtered %>%
  count(word1, word2, sort = TRUE) %>% 
  filter(!is.na(word1))

top_20_bigrams <- head(bigram_ct, 20)
```

```{r show_results_2, results='show'}
formattable(top_20_bigrams, 
            align =c("c","c","c","c","c", "c", "c", "c", "r"), 
            list(
              `Top 20 Bigrams` = formatter(
              "span", style = ~ style(color = "black",font.weight = "bold")),
              `n`= color_tile("cadetblue1", "dodgerblue2")

))
```

## Plot Top 20 Bigrams

```{r}
bigram_ct_toplot <- head(bigram_ct,20) %>%
  mutate(bigram = paste0(word1, " ", word2)) %>%
  mutate(n = as.numeric(n))

bi_plot <- ggplot(data=bigram_ct_toplot, aes(fill = n, x = reorder(bigram, n), y = n)) +
  geom_col() +
  scale_y_continuous(breaks = seq(0, 300, by = 25)) +
  labs(y = NULL, 
       x = "Bigram") + 
  coord_flip() +
  ggtitle("Top 20 Bigrams in Articles mentioning Domestic Violence\npublished in The Windy City Times") + 
  theme(legend.position="none") + 
  expand_limits(x = 0, y = 0)

plot(bi_plot)
```

### Initial Findings: 
Several queer distinctive terms stand out: 
- lgbt community
- hiv aids
- sexual orientation
- openly gay
- gays lesbians 
- lgbtq community
- marriage equality
- gender identity
- lgbt people

Several other LGBT issues seems to be intermixed with domestic violence, like "marriage equality" and "human rights" and "hiv aids". Maybe domestic violence is less likely to get articles just dedicated to it as an issue, and more likely to be mentioned among many issues that the LGBTQ community faces. 

It seems like avocacy groups are involved in queer DV: 
- executive director
- amigas latinas
- illinois united

### Map years

```{r}
year_df <- clean_df %>%
  select(year, index) %>%
  distinct() %>%
  count(year)

year_plot <- ggplot(data=year_df, aes(year, n, fill = n)) +
  geom_col() +
  labs(y = NULL, 
       x = "year") + 
  ggtitle("Articles over time mentioning Domestic Violence\npublished in The Windy City Times") + 
  theme(legend.position="none") 

plot(year_plot)
```

### Initial Findings

2012 should be looked at as a year when possibly a prominent domestic violence case occured in Chicago, which might explain the spike in coverage.
N is small, but unclear why the drop off in covereage in 2021 and 2022, especially as DV increased as an issue with Covid. 

# topic modeling
```{r}
# create new dataframe from cleaned data to have just the text
textdata <- clean_df %>% 
  select(filename, text, year) %>% 
  as.data.frame() %>% 
  rename(doc_id = filename, text= text)

# load stopwords
english_stopwords <- readLines("https://slcladal.github.io/resources/stopwords_en.txt", encoding = "UTF-8")
# create corpus object
corpus <- Corpus(DataframeSource(textdata)) 
# Preprocessing chain
processedCorpus <- tm_map(corpus, content_transformer(tolower))
processedCorpus <- tm_map(processedCorpus, removeWords, english_stopwords)
processedCorpus <- tm_map(processedCorpus, removePunctuation, preserve_intra_word_dashes = TRUE)
processedCorpus <- tm_map(processedCorpus, removeNumbers)
processedCorpus <- tm_map(processedCorpus, stemDocument, language = "en")
processedCorpus <- tm_map(processedCorpus, stripWhitespace)
```

```{r tm3a}
#DTM: rows correspond to the documents in the corpus. Columns correspond to the terms in the documents. Cells correspond to the weights of the terms. (Girder)
# compute document term matrix with terms >= minimumFrequency
minimumFrequency <- 5
DTM <- DocumentTermMatrix(processedCorpus, control = list(bounds = list(global = c(minimumFrequency, Inf))))
# have a look at the number of documents and terms in the matrix
dim(DTM)
# due to vocabulary pruning, we have empty rows in our DTM
# LDA does not like this. So we remove those docs from the
# DTM and the metadata
sel_idx <- slam::row_sums(DTM) > 0
DTM <- DTM[sel_idx, ]
textdata <- textdata[sel_idx, ]
``` 

### Articles per year

```{r}
articles_years <- textdata %>% 
  distinct(doc_id, .keep_all=TRUE) %>% 
  count(year) %>% 
  mutate(pct_total= (n/sum(n))) %>% 
  mutate(pct_total= formattable::percent(pct_total)) %>% 
  mutate(pct_total = round(pct_total, 1)) %>% 
  arrange(desc(year))

library(kableExtra)
articles_years %>%
  kbl(caption = "DV Windy City Times Articles by Year (n=270, 11/27/2024)", font_size = 30) %>%
  kable_classic(full_width = F, html_font = "Cambria") %>% 
  column_spec(1, bold = T, border_right = T) %>%
  column_spec(2, width = "5em") %>% 
  column_spec(3, width = "5em", background = "yellow") 
```

### Topic modeling continued

```{r tm12}
# number of topics
# K <- 20
K <- 6
# set random number generator seed
set.seed(9161)
#Latent Dirichlet Allocation, LDA
topicModel2 <- LDA(DTM, K, method="Gibbs", control=list(iter = 500, verbose = 25, alpha = 0.2))
tmResult <- posterior(topicModel2)
theta <- tmResult$topics
beta <- tmResult$terms
topicNames <- apply(terms(topicModel2, 10), 2, paste, collapse = " ")  # reset topicNames
```

### Mean topic proportions per yaer

```{r}
# Step 1: Check dimensions
n_theta <- nrow(theta)
n_textdata <- length(textdata$year)

cat("Number of rows in theta: ", n_theta, "\n")
cat("Number of documents in textdata: ", n_textdata, "\n")

# Check if textdata contains all the documents in theta
common_ids <- intersect(rownames(theta), textdata$doc_id) # Assuming textdata has a 'doc_id' column

# Filter textdata to include only the documents present in theta
textdata_filtered <- textdata[textdata$doc_id %in% common_ids, ]

# Check dimensions after filtering
n_textdata_filtered <- nrow(textdata_filtered)
cat("Number of documents in filtered textdata: ", n_textdata_filtered, "\n")

# Ensure the lengths match now
if (n_theta != n_textdata_filtered) {
  stop("The number of rows in 'theta' still does not match the length of 'textdata_filtered$year'.")
}

# Align rownames of theta with filtered textdata
theta_aligned <- theta[rownames(theta) %in% textdata_filtered$doc_id, ]

# Optional: Verify the order of documents
if (!all(rownames(theta_aligned) == textdata_filtered$doc_id)) {
  # If the order doesn't match, reorder one to match the other
  textdata_filtered <- textdata_filtered[match(rownames(theta_aligned), textdata_filtered$doc_id), ]
}

# Ensure they are now aligned and can be combined
if (!all(rownames(theta_aligned) == textdata_filtered$doc_id)) {
  stop("The document IDs still do not match. Please check the data alignment.")
}

# Step 2: Combine data
topic_data <- data.frame(theta_aligned, year = textdata_filtered$year)

# Step 3: Aggregate data
topic_proportion_per_year <- aggregate(. ~ year, data = topic_data, FUN = mean)

# get mean topic proportions per year
# topic_proportion_per_year <- aggregate(theta, by = list(year = textdata$year), mean)
# set topic names to aggregated columns
colnames(topic_proportion_per_year)[2:(K+1)] <- topicNames
# reshape data frame
vizDataFrame <- melt(topic_proportion_per_year, id.vars = "year")
```

### Examine topic names

```{r show_results, results='show'}
#enframe(): Converts a named list into a dataframe.
topics <- enframe(topicNames, name = "number", value = "text") %>% 
  unnest(cols = c(text)) 
  
topics <- topics %>%
  kbl() %>%
  kable_styling()

topics
```

### Initial Findings

I experimented with changing k and found 6 created topic groups that made the most sense, and I leaned towards keeping k low to avoid overfitting on a small dataset. 

community_org - 1 - chicago work communiti organ lgbt center servic health univers youth

theater - 2 - chicago show perform music gay theatr center event featur halst

elect - 3 - state illinoi counti gay unit race marriag cook elect district

domestic_abuse - 4 - violenc peopl women domest communiti sexual black queer abus report

legal - 5 - number law polic offic case peopl year report hiv charg

life - 6 - peopl time year work famili life make love wct thing


Community_orgs makes sense if non-profit groups are involved in DV service work. 

Theater suggests that articles about DV are intermingled with other topics; I found several articles that were just a calendar of monthly events. I suspect there is some regular DV related event. 

Elect suggests there was a local election where DV was an issue that came up. 

Domestic abuse and Legal seem the most topical. 

And life is confusing as a topic. Honestly I'm not sure what to call it or what it is capturing. 


### Review the topics and determine a 1-2 word label after reading the source documents.

```{r}
theta2 <- as.data.frame(theta)

topic1 <- theta2 %>% 
  rownames_to_column(var = "file") |> # putting the rownames into a new column called file
  mutate(file = str_remove(file, "^X"),  # Remove leading 'X'
         line = str_extract(file, "(?<=\\.txt)\\.\\d+")) |>   # Extract number after .txt
  mutate(file = str_remove(file, "\\.\\d+$")) |> 
  rename(topic1 = '1') |> 
  top_n(20, topic1) |> 
  arrange(desc(topic1)) |>  
  select(file, line, topic1) 
```

### Add categories
```{r}
#add categories
vizDataFrame <- vizDataFrame %>% 
  mutate(category = case_when(
    str_detect(variable,  "chicago work communiti organ lgbt center servic health univers youth") ~ "community_org",
    str_detect(variable, "chicago show perform music gay theatr center event featur halst") ~ "theater",
    str_detect(variable, "state illinoi counti gay unit race marriag cook elect district") ~ "elect",
    str_detect(variable, "violenc peopl women domest communiti sexual black queer abus report") ~ "domestic_abuse",
     str_detect(variable, "number law polic offic case peopl year report hiv charg") ~ "legal",
    str_detect(variable, "peopl time year work famili life make love wct thing") ~ "life",
    ))
```

# Fact Check and Validate Topics

### For community_org
```{r}
theta2 <- as.data.frame(theta)

community_org <- theta2 %>% 
  #renaming for a general topic
  rename(community_org = '1') %>% 
  top_n(20, community_org) %>%
  arrange(desc(community_org)) %>% 
  select(community_org)

# Apply rownames_to_column
community_org  <- tibble::rownames_to_column(community_org, "story_id") 

community_org$story_id <- gsub("X", "", community_org$story_id)
```


### For legal
```{r}
legal <- theta2 %>% 
  #renaming for a general topic
  rename(legal = '5') %>% 
  top_n(20, legal ) %>%
  arrange(desc(legal )) %>% 
  select(legal )

# Apply rownames_to_column
legal  <- tibble::rownames_to_column(legal , "story_id") 

legal $story_id <- gsub("X", "", legal $story_id)
```


### For domestic_abuse
```{r}
domestic_abuse <- theta2 %>% 
  #renaming for a general topic
  rename(domestic_abuse = '4') %>% 
  top_n(20, domestic_abuse ) %>%
  arrange(desc(domestic_abuse )) %>% 
  select(domestic_abuse )

# Apply rownames_to_column
domestic_abuse  <- tibble::rownames_to_column(domestic_abuse , "story_id") 

domestic_abuse $story_id <- gsub("X", "", domestic_abuse $story_id)
```

### Figure 3: Common Narratives in Windy City Times articles mentioning domestic violence

```{r}
# plot topic proportions per decade as bar plot
ggplot(vizDataFrame, aes(x=year, y=value, fill=category)) + 
  geom_bar(stat = "identity") + ylab("proportion") + 
  scale_fill_manual(values = paste0(alphabet(20), "FF"), name = "year") + 
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
   scale_fill_manual(values=c("#9933FF",
                              "#33FFFF",
                              "red",
                              "yellow",
                              "darkblue",
                              "green"))+
  labs(title = "Common Narratives in Windy City Times articles mentioning domestic violence",
       subtitle = "Six probable topics in article sample. n=270",
       caption = "Aggregate mean topic proportions per year. Graphic by Marilyn Harbert, 11-30-2024")
```

### Initial Findings:

There seems to be consistency in topic coverage in years with enough articles to make a judgement. 


# Sentiment Analysis

```{r}
get_sentiments("afinn")

load("../Summary_HW/data/afinn.rda")
```

### Initial NRC joining
```{r}
nrc_articles <- get_sentiments("nrc") 

tidy_articles <- clean_df %>%
  unnest_tokens(word, text) 

tidy_articles %>%
  inner_join(nrc_articles) %>%
  count(word, sort = TRUE)

```

### Plot Bing sentiment analysis

```{r}
bing_articles <- tidy_articles %>%
  inner_join(get_sentiments("bing")) %>%
  count(index, sentiment) %>%
  pivot_wider(names_from = sentiment, values_from = n, values_fill = 0) %>% 
  mutate(sentiment = positive - negative)
```

```{r}
ggplot(bing_articles, aes(index, sentiment)) +
  geom_col(show.legend = FALSE) 
```

### Initial Findings

More positive words than negative. This suggests low density of coverage of DV in articles mentioning it, as DV is a negative subject. Alternately, the sentiment analysis may not be picking up the negativity of the words associated with DV. 

```{r, include = FALSE}
afinn <- tidy_articles %>% 
  inner_join(get_sentiments("afinn")) %>% 
  group_by(index) %>% 
  summarise(sentiment = sum(value)) %>% 
  mutate(method = "AFINN")

bing_and_nrc <- bind_rows(
  tidy_articles %>% 
    inner_join(get_sentiments("bing")) %>%
    mutate(method = "Bing et al."),
  tidy_articles %>% 
    inner_join(get_sentiments("nrc") %>% 
                 filter(sentiment %in% c("positive", 
                                         "negative"))) %>%
    mutate(method = "NRC")) %>%
  count(method, index, sentiment) %>%
  pivot_wider(names_from = sentiment,
              values_from = n,
              values_fill = 0) %>% 
  mutate(sentiment = positive - negative)


#bind_rows(afinn, bing_and_nrc) %>%
#  ggplot(aes(index, sentiment, fill = method)) +
#  geom_col(show.legend = FALSE) +
#  facet_wrap(~method, ncol = 1, scales = "free_y")

```

### Bing top words count
```{r show_results_4, results='show'}
bing_word_counts <- tidy_articles %>%
  inner_join(get_sentiments("bing")) %>%
  count(word, sentiment, sort = TRUE) %>%
  ungroup()

bng_cnts <- head(bing_word_counts, 20) %>%
  kbl() %>%
  kable_styling()

bng_cnts
```

### Initial Findings

## Queer = negative, Intimate = positive

1. Categorizing queer as negative is homophobic.

2. This might not be the tool for me. 

With the specific language used in the articles I'm analyzing, like terms like "intimate partner violence" end up categorized as positive because "intimate" is categorized as positive. This might be a hammer when I need a laser. 

Additionally, I'm confused why "skinny" is so high up on the list of words?


## Words left out of sentiment analysis 
```{r show_results_3, results='show'}
left_out <- tidy_articles %>%
  anti_join(get_sentiments("bing")) %>%
  filter(!word %in% stop_words$word) %>%
  count(word, sort = TRUE) %>%
  ungroup()

lft_out <- head(left_out, 20) %>%
  kbl() %>%
  kable_styling()

lft_out
```

### Initial Findings

Above is the list of terms left out of the sentiment analysis I conducted with Bing. 

Key terms like "community", "violence", "domestic" and "hiv" are left out, which points to the small size of the sentiment analysis dataset. It misses key very frequent terms, and with that misses a lot of the sentiment in the articles. 



# THANK YOU

# FEEDBACK WELCOME
