---
title: "MH_Assignment1_Basic_R_proficiency"
author: "Marilyn Harbert"
date: "2024-09-19"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

--Load relevant software libraries

```{r}
#loading the libraries
library(rio)
library(janitor)
library(tidyverse)
library(tidytext)

```

--Load the data: https://github.com/wellsdata/CompText_Jour/blob/main/data/blackindex_master.csv

```{r}
# loading the dataset
blackindex_master <- rio::import("https://github.com/wellsdata/CompText_Jour/raw/main/data/blackindex_master.csv") 

```

--Using code, describe the number of rows and columns in the dataset

```{r}
glimpse(blackindex_master)
```

--Create a table that displays a count of the top 5 newspaper_city entries

```{r}

top_5_newspaper_cities <- blackindex_master %>%
  select(newspaper_city) %>%
  group_by(newspaper_city) %>%
  count() %>%
  arrange(desc(by=n)) %>%
  head(5)

```

--Create a table that counts the different entries in the "newspaper_city" column

```{r}

newspaper_cities <- blackindex_master %>%
  select(newspaper_city) %>%
  group_by(newspaper_city) %>%
  count() %>%
  arrange(desc(by=n)) 

```

--Create a table that counts all newspaper_city entries by year. UPDATE: Filter out the NA values

```{r}

year_newspaper_cities <- blackindex_master %>%
  select(newspaper_city, year) %>%
  filter(!is.na(newspaper_city)) %>%
  group_by(newspaper_city, year) %>%
  count() 


```

--Create a simple column ggplot chart that shows the total entries by year

```{r}

entries_by_year <- blackindex_master %>%
  count(year) %>%
  ggplot(aes(x = year, y = n)) +
      geom_col(position = "dodge") + 
      theme(legend.position = "none") +
#This is your title sequence
      labs(title = "Number of newspaper articles mentioning lynching by year",
          caption = "Graphic by Marilyn Harbert, 09-21-2024",
          y="Number of Newspaper Articles",
          x="Year")

plot(entries_by_year)


```

Armed with your data analysis, write a 250 word memo at the end of the R markdown document that summarizes your findings. Use this opportunity to ask questions or note any major flaws in the data.


I struggle to come to any conclusions at all about the data because I am so removed from the sourcing of the data. The lack of metadata means I have very little context wtithin which to judge the results of our data manipulation and visualization. If I knew from what selection of articles this was drawn, what keywords were used for the search, and what exclusions were made, I might be able to start to draw conclusions. 

Within the data we have, the number of entries rises until it reaches its peak at about 1920, and then fluctuates until dropping off to only a few per year around 1960. 

To draw additional conclusions, questions I might like answered include: 
- What search terms were used to get these results?
- What newspapers are included (and thus which are excluded) from this database?
- What year does this database start at, and what year does it end at?
- What database are these article drawn from?









