---
title: "MH_Homework_ScrapePDF"
author: "Marilyn Harbert"
date: 2024-10-22
output: html_document
---

Homework: 
1) Download this PDF: https://github.com/wellsdata/CompText_Jour/blob/main/exercises/assets/pdfs/AI_yao_taufiq.PDF

2) Create a new R Markdown document.

3) Extract the text using the pdftools package

4) Split the text so you have one article per file

5) Construct a dataframe with an index of the articles a unique file name for each article

6) Pull the text articles together into a single dataframe, one row per sentence

7) BONUS NERD ZONE: Link the dataframe with the text to the index

```{r}
#load libraries

library(quanteda)
library(readtext)
library(tidyverse)
library(pdftools)
```

3) Extract the text using the pdftools package
```{r}
text <- pdf_text("AI_yao_taufiq.PDF")
#pdf_text reads the text from a PDF file.
writeLines(text, "homework_pdf_import.txt")

```

4) Split the text so you have one article per file
```{r}

file_path <- "homework_pdf_import.txt"
text_data <- readLines(file_path)

# Step 2: Combine lines into one single string
text_combined <- paste(text_data, collapse = "\n")

# Step 3: Split the text by the "End of Document" phrase
documents <- strsplit(text_combined, "End of Document")[[1]]

# Step 4: Write each section to a new file
output_dir <- "../completed_homework/"
for (i in seq_along(documents)) {
  output_file <- file.path(output_dir, paste0("homework_pdf_", i, ".txt"))
  writeLines(documents[[i]], output_file)
}

cat("Files created:", length(documents), "\n")

```

5) Construct a dataframe with an index of the articles a unique file name for each article
```{r}

extracted_lines <- read_lines("../completed_homework/homework_pdf_1.txt")

# Print the extracted lines to the console
cat(extracted_lines, sep = "\n")

extracted_lines <- extracted_lines |> 
  as.data.frame() 


extracted_lines <- extracted_lines |> 
  mutate(extracted_lines = str_remove(extracted_lines, "\\| About LexisNexis \\| Privacy Policy \\| Terms & Conditions \\| Copyright © 2020 LexisNexis"))

# Step 1: Trim spaces and detect rows with titles and dates
cleaned_data <- extracted_lines |>
  mutate(
    # Trim leading and trailing spaces before detection
    trimmed_line = str_trim(extracted_lines),  

    # Detect titles (start with a number and a period)
    is_title = str_detect(trimmed_line, "^\\d+\\. "),  

    # Detect dates (e.g., "Aug 14, 2024")
    is_date = str_detect(trimmed_line, "\\b\\w{3} \\d{1,2}, \\d{4}\\b")
  )


# Step 2: Shift dates to align with corresponding titles
aligned_data <- cleaned_data |>
  mutate(
    date = ifelse(lead(is_date, 1), lead(trimmed_line, 1), NA_character_)  # Shift date to title's row
  ) |>
  filter(is_title) |>
  select(trimmed_line, date)  # Keep only the relevant columns

# Step 3: Rename columns for clarity
final_data <- aligned_data |>
  rename(
    title = trimmed_line,
    date = date
  )

#Step 4: Date and Publication in separate columns, and formatted
final_data <- separate(data = final_data, col = date, into = c("date2", "publication"), sep = "  ", extra = "merge", fill = "right")


#Step 5: Format date, clean headline
final_data <- final_data |> 
  mutate(date = as.Date(date2,format = "%b %d, %Y")) |> 
  mutate(title =str_remove(title, "^\\d+\\. ")) |> 
  subset(select = -(date2)) |> 
  mutate(index = row_number()) |> 
  select(index, date, title, publication)



#unique file name each article
final_data <- final_data %>%
  mutate(unique_file_name = paste(final_data$index, final_data$title)) %>%
  mutate(unique_file_name = str_replace_all(unique_file_name, " ", "_")) 



write_csv(final_data, "../completed_homework/final_data.csv")



```

6) Pull the text articles together into a single dataframe, one row per sentence
```{r}

file_path <- "homework_pdf_import.txt"
text_data <- readLines(file_path)

df_text_data <- as.data.frame(text_data)

cleaned_df_text_data <- df_text_data %>%
  rename(sentences = text_data) %>%
  mutate(sentences = str_trim(sentences, side = "both")) %>%
  filter(!grepl('[0-9]', sentences)) %>%
  filter(!sentences == "") 


```
